% A group contains $N$ individuals, where each individual $i$ has a position vector $\boldsymbol{c}_i(t)$, direction as a scalar $d_i(t)$ defined as counter-clockwise angle from the positive x-axis, and speed $s$. 
% The individuals avoid collisions with their neighbors by turning away from individuals $j$ within distance $\alpha$ according to
% \begin{equation}
% d_i (t+\Delta t) = \arg \left(- \sum_{j \neq i} \frac{\boldsymbol{c}_j (t) - \boldsymbol{c}_i (t)}{|\boldsymbol{c}_j (t) - \boldsymbol{c}_i (t) |}\right),
% \label{eq:repulsion}
% \end{equation}
%  where $\arg$ refer to angle to the positive x-axis of of the resulting vector inside the parenthesis and $d_i(t)$ is the desired direction of motion. 
%  If there are no neighbors within distance $\alpha$, the individuals will move towards individuals $j$ within distance $\rho$ according to
% \begin{equation}
% d_p (t) = \arg \left(\sum_{j \neq i} \frac{\boldsymbol{c}_j (t)- \boldsymbol{c}_i (t)}{|\boldsymbol{c}_j (t) - \boldsymbol{c}_i (t)|} \right),
% \label{eq:dp}
% \end{equation}

% \begin{equation}
% d_d (t) = \text{mean}\left( \sum_{j = 1} d_j (t) \right),
% \label{eq:dd}
% \end{equation}

% \begin{equation}
% d_i (t+\Delta t) = \frac{d_p (t) + d_d (t)}{2}.
% \label{eq:attraction}
% \end{equation}
% Here $d_p$ is the direction from individual $i$ to individual $j$, and $d_d$ is the mean value of the directions of the individuals $j$.
% A proportion $p$ of the individuals know in which direction $g$ to go, and their desired direction is given by
% \begin{equation}
% d_i^\prime (t+\Delta t) = d_i (t+\Delta t) + \omega (g - d_i (t+\Delta t)),
% \label{eq:attraction}
% \end{equation}
% where $\omega$ decides the influence of the known direction $g$; $\omega=0$ makes the individual move only by social interaction and the higher the value of $\omega$, the more the individual moves in the known direction.
% \\\\
% A small random angle $\theta$ is added to 

A group contains $N$ individuals, where each individual $i$ has a position vector $\boldsymbol{c}_i(t)$, direction vector $\boldsymbol{v}_i(t)$ and speed $s$. 
The individuals avoid collisions with their neighbors by turning away from individuals $j$ within distance $\alpha$ according to
\begin{equation}
\boldsymbol{d}_i (t+\Delta t) = - \sum_{j \neq i} \frac{\boldsymbol{c}_j (t) - \boldsymbol{c}_i (t)}{|\boldsymbol{c}_j (t) - \boldsymbol{c}_i (t) |},
\label{eq:repulsion}
\end{equation}
where $\boldsymbol{d}_i(t)$ is the desired direction of motion. 
If there are no neighbors within distance $\alpha$, the individuals will move towards individuals $j$ within distance $\rho$ according to
\begin{equation}
\boldsymbol{d}_i (t+\Delta t) = \sum_{j \neq i} \frac{\boldsymbol{c}_j (t)- \boldsymbol{c}_i (t)}{|\boldsymbol{c}_j (t) - \boldsymbol{c}_i (t)|} + \sum_{j = 1} \frac{\boldsymbol{v}_j (t)}{|\boldsymbol{v}_j (t)|}.
\label{eq:attraction}
\end{equation}
The direction $\boldsymbol{d}_i(t)$ is normalized to a unit vector $\hat{\boldsymbol{d}}_i(t)$. 
A proportion $p$ of the individuals know in which direction $\hat{\boldsymbol{g}}$ to go, and their desired direction is given by
\begin{equation}
\boldsymbol{d}_i^\prime (t+\Delta t) = \frac{\hat{\boldsymbol{d}}_i (t+\Delta t) + \omega \hat{\boldsymbol{g}}}{|\hat{\boldsymbol{d}}_i (t+\Delta t) + \omega \hat{\boldsymbol{g}}|},
\label{eq:attraction}
\end{equation}
where $\omega$ decides the influence of the known direction $\hat{\boldsymbol{g}}$; $\omega=0$ makes the individual move only by social interaction and the higher the value of $\omega$, the more the individual moves in the known direction.

\subsection{Movement} % (fold)
\label{sub:movement}
The direction of each individual is rotated by a small random angle, picked from a normal distribution with mean zero and standard deviation $\sigma = 0.01$, in order to simulate stochastic behaviors of the group.
\\\\
In each time step an individual can change its direction by a maximum angle of $\theta \Delta t$. 
If the difference between its calculated wanted new direction $\boldsymbol{d}_i''$ and its current direction is lower than $\theta \Delta t$, its velocity will be set to $\boldsymbol{v}_i(t + \Delta t) = \boldsymbol{d}_i''$.
If it is higher, the individual will be changing its direction angle with $\theta \Delta t$ towards direction $\boldsymbol{d}_i''$. 
The new velocity $\boldsymbol{v}_i(t + \Delta t)$ will then be used to calculate the new position, as 
\begin{equation}
	\boldsymbol{c}_i(t+\Delta t) = \boldsymbol{c}_i(t) + \boldsymbol{v}_i(t + \Delta t)\Delta t s_i,
\end{equation}
where $s_i$ is the speed of the individual.
% subsection movement (end)

\subsection{Elongation} % (fold)
\label{sub:elongation}
A bounding box is calculated for given time steps, which is defined as the smallest box that can contain all individuals in the simulations, having one side parallel to the mean direction of the group in that time step, and the other side perpendicular.
The elongation is defined as the length of the parallel side divided the length of the perpendicular side.
% subsection elongation (end)

\subsection{Accuracy} % (fold)
\label{sub:accuracy}
The accuracy of the group is defined as 
\begin{equation}
	\hat{a} = \text{mean} ((h - g)^2),
\end{equation}
where $h$ is the group direction angle, in relation to the positive x-axis, and $g$ is the angle to food in relation to the positive x-axis, so that for a completely random direction of the group, an average of 0.5 would be expected. After this, a normalization was done to have values between 0 and 1, as
\begin{equation}
	a = 2(\hat{a} - 0.5).
\end{equation}
% subsection accuracy (end)